---
title: "Untitled"
output: html_document
---


```{r}

library(tidyverse)
library(MASS)

```

```{r}
# Reading the data:
df <- read_rds(file = "/Users/caeciliaskov-jensen/Documents/Uni/8. semester/Statistical and Machine Learning/16. Predictions/ALS_data_regression/ALS_progression_rate.1822x370.rds") 

```

# Quick view of all data

```{r}

df[1:10,1:10]

```

# Split into training and prediction set

```{r}

set.seed(0)

data_train    <- df %>% filter(!is.na(dFRS))
data_predict  <- df %>% filter(is.na(dFRS))

```

# Finding the best model to predict

```{r}

trainfold <- data_train %>% sample_frac(size = 0.8)
testfold <- setdiff(data_train, trainfold)

# Making the model from out first round of submissions:
ALS_model <- lm(dFRS ~., data = df)

# Getting summary of the model fit using AIC:
fit <- stepAIC(ALS_model, direction = "forward", trace = FALSE)
summary(fit)


```

```{r}

# Fitting the new model with the predictors with significant p-values:
ALS_model2 <- lm(dFRS ~ Onset.Delta + Son + meansquares.alsfrs.score + meansquares.speech + sum.svc.liters + max.bp.diastolic, data = df)

```


# Test error

```{r}

# We predict on the test fold
predicted <- predict(ALS_model2, newdata = testfold)

# We compare with the observed values and calculate RMSE
observed  <- testfold$dFRS
mse       <- mean((observed-predicted)^2)
(rmse     <- sqrt(mse))

test_rmse <- rmse # Our guess on the general rmse of the model (very unprecise!)

```

# Accuracy using cross validation

```{r}
cv_rmse <- function(x, k, r){
  train_control <- trainControl(method = "repeatedcv", number = k, repeats = r)
  model <- train(dFRS ~ Onset.Delta + Son + meansquares.alsfrs.score + meansquares.speech + sum.svc.liters + max.bp.diastolic, data = x, method = "lm", trControl = train_control)
  return(model)
}

cv_rmse(data_train, 10, 10)

```

# Predict the real unknown data

First we fit the model to all of our known data

Then we predict on the unknown data

The predictions must have the following column and the row order must be the same as the original!

* predicted (the predicted class, either "Normal" or "Tumor")

```{r}
predicted <- predict(ALS_model2, newdata = data_predict)

submission <- tibble(predicted)

head(submission)

```
# Submitting your answer

The following code will give us

* your chosen team name
* the name of the people on the team
* your estimated error rate (from train/test or CV or similar)
* your predictions

Please edit the values below.

The filename of the output will be automated minitcga_cancer_classification.TEAMNAME.rds

Please - do not use space or funny letters in your team name.

```{r}

team_name        <- "LCPSoundsystem"
team_people      <- c("Peter", "Cæcilia", "Lea")
team_error_rate  <- test_rmse
team_predictions <- submission

#
# Always run this code
# If it fails you have done something wrong!
#
# Extract the columns needed
library(dplyr)
team_predictions <- subset(team_predictions, select = predicted)

# Save all the stuff in one object
write_rds(x = list(team_name, team_people, team_error_rate, team_predictions), 
          path = paste("minitcga_cancer_classification.", team_name, ".rds", sep=""))

```

